### 2022-01-02 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_neutral_landscapes_jl@76c7b9ade5287eadc68d40ada1fbf3e0bf59a123 🚀
Deploying to gh-pages from @ gottacatchenall/ms_neutral_landscapes_jl@2097f05e0a19cd9b458269edabf1cd524a42f668 🚀

@@

In this section we show our implementation of MPD is faster than NLMR's
C++ MPD across all scales, up to the asyptotic limit imposed by the
\(O(n^2)\) scaling of the raster

\begin{figure}
\centering
\includegraphics{./figures/draftfig3.png}
\caption{Comparison of speed of generating a midpoint displacement
neutral landscape (y-axis) against raster size (measured as length of
the size of a square raster, x-axis)}
\end{figure}

>>>>

\begin{longtable}[]{@{}llllll@{}}
\toprule
Model & nlmpy? & NLMR & Description & Reference & Aliases\tabularnewline
\midrule
\endhead
No gradient & x & x & & &\tabularnewline
Planar gradient & x & x & & &\tabularnewline
Distance gradient & x & x & & &\tabularnewline
Random rectuangular cluster & x & x & & &\tabularnewline
Random element nearest-neighbor & x & x* & & & \texttt{nlm\_mosaictess},
k-means\tabularnewline
Random cluster nearest-neighbor & x & x & & &\tabularnewline
Random curds & & x & & &\tabularnewline
Gaussian Field & & x & & &\tabularnewline
Perlin noise & x & & & &\tabularnewline
Diamond-square & & & & &\tabularnewline
Mosaic random field & & x & & &\tabularnewline
\bottomrule
\end{longtable}

@@

In this section we show our implementation of MPD is faster than NLMR's
C++ MPD scales until the asyptotic limit imposed by the \(O(n^2)\)
scaling of the raster

\begin{figure}
\centering
\includegraphics{./figures/figure3.png}
\caption{Comparison of speed of generating a midpoint displacement
neutral landscape (y-axis) against raster size (measured as length of
the size of a square raster, x-axis)}
\end{figure}
